\documentclass[]{article}
\usepackage{parskip} %Removes paragraph line indents

%opening
\title{Group Assignment\\ \ \\Compilers\\ \ \\}
\author{Oliver Mikkel Winther Cristensen (klw741) \\ \ \\Mathias Brøndum Leroul (swn848)\\ \ \\Sebastian O. Jensen (gjx653)\\ \ \\}
\date{Turn-in date: 18-12-2015}

\begin{document}

\maketitle
\newpage

\textbf{Contents of the Report}\\
It is largely up to you to decide what you think is important to include in the report, as long as
the following requirements are met:
Your report should justify all your changes to the compiler modules, in particular, the lexer,
parser, interpreter, type checker, machine-code generator, and the optimization modules. All
major design decisions should be presented and justified.
When evaluating your work, the main focus will be on verifying that your implementation
of the language is correct. While we do not put particular emphasis on compiler optimizations
in this course, we will also evaluate the quality of the generated code: if there are obvious
inefficiencies that could have been easily solved you will be penalized, as they testify either
wrong priorities or lack of understanding.
You should not include the whole compiler in your report, but you must include the parts
that were either added, i.e. new code, or substantially modified. Add them as code listings, and
use the appendix if they get too big. Ideally, we should not need to read your source code.
Your report should describe whether the compilation and execution of your input/test (FASTO)
programs results in the correct/expected behavior. If it does not, try to explain why this is. In
addition, (i) it must be assessed to what extent the delivered test programs cover the language
features, and (ii) if the implementation deviates from the correct/expected behavior than the test
program(s) should illustrate the implementation shortcomings to your best extent.
Known shortcomings in type checking and machine-code generation must be described, and,
whenever possible, you need to make suggestions on how these might be corrected.
The report should not exceed this document in size, and should have an appropriate level of
detail. You might be penalized if your report includes too many irrelevant details.

\section{Introduction}
	We're given the grand task of 
\section{Implementation}
	\subsection*{Notes}
		\begin{itemize}
			\item Implemented Boolean Litterals: true and false.
			\subitem Added test files bool.fo, bool.in, bool.out
		\end{itemize}
	
\section{Results}
\section{Conclusion}

\end{document}
